\large{McGill University | Desautels Faculty of Management}\\ \hfill \break \hfill \break \hfill \break \hfill \break \\\Large MGSC 670 - Revenue Management\\ \textbf{Group Assignment 1: Markdown Strategy}\\ \hfill \break \hfill \break

### 2023-05-16 manuscript/manuscript.tex
updated pseudo code

\begin{algorithmic}[1]
    \Procedure{Simulate}{$means\ per\ price,\ stdev\ per\ price$}
        \For{week in length($means\ per\ price$)}
            \State \textbf{generate} unit sales \textbf{with} mean, stdev
        \EndFor
        \State \textbf{return} unit sales
    \EndProcedure
    \State 
    \Procedure{Test Policy}{$policy,\ list\ of\ unit\ sales$}
        \For{t = 1 to 15}
            \State \textbf{generate} price at week t+1 from $policy$ logic
        \EndFor
        \State \textbf{return} price at week t+1
    \EndProcedure
    \State
    \For{policy in policy candidate list}
        \For{t = 1 to 100}
            \State list of unit sales = $Simulate$ (price mean, price stdev) 
            \State policy results = $Test\ Policy$ (policy, list of unit sales) 
        \EndFor
    \EndFor
\end{algorithmic}

@@

\begin{algorithmic}[1]
    \Procedure{Policy Validate}{$policy$}
        \State URL = "http://www.randhawa.us/games/retailer/nyu.html"
        \State expected return = \textbf{with} URL \textbf{use} $policy$ for t+1 decision
        \State \textbf{return} expected return
    \EndProcedure
    \State
    \For{policy in policy candidate list}
        \For{t = 1 to 100}
            \State policy results = $Policy\ Validate$ (policy) 
        \EndFor
    \EndFor
    \State \textbf{plot} policy results
\end{algorithmic}

@@

>>>>

\begin{algorithmic}[1]
    \Procedure{Policy}{$list\ of\ sales,\ list\ of\ price$}
        \State \textbf{generate} price for the next period \textbf{with} current run sales and prices
        \State \textbf{return} price
    \EndProcedure
    \State
    \Procedure{Simulate}{$policy,\ means\ per\ price, stdevs\ per\ price$}
        \For{t = 1 to 15}
            \State \textbf{generate} unit sales \textbf{with} mean, stdev, and current price
            \State \textbf{generate} price \textbf{for} next period \textbf{with} given policy
        \EndFor
        \State \textbf{return} revenue
    \EndProcedure 
    \State
    \For{policy \textbf{in} policy candidate list}
        \For{t = 1 to 100}
            \State \textbf{generate} means per price, stdevs per price \textbf{for} current simulation run 
            \State policy results = $Simulate$ (policy, means per price, stdevs per price) 
            \State \textbf{save} policy results
        \EndFor
    \EndFor
\end{algorithmic}

@@

\begin{algorithmic}[1]
    \Procedure{Policy Validate}{$policy$}
    \State URL = "http://www.randhawa.us/games/retailer/nyu.html"
    \For{ t= 1 to 15}
        \State \textbf{retrieve} unit sales \textbf{from} website
        \State \textbf{generate} price \textbf{for} next period \textbf{with} given policy
    \EndFor
    \State \textbf{return} expected return
    \EndProcedure
    \State
    \For{policy in policy candidate list}
        \For{t = 1 to 100}
            \State policy results = $Policy\ Validate$ (policy) 
        \EndFor
    \EndFor
    \State \textbf{plot} policy results
\end{algorithmic}

@@

Figure 5 demonstrates the relationship between prices and sales in different policies. 
Policies with better performance such as Naïve Adaptive Likelihood, Likelihood Demand Trend Projection, and Moving Average Naïve, share a common characteristic: adopting price change steadily. 
These models take more time waiting and observing the market before adjusting prices accordingly. 
Conversely, Long Term Adaptive Moving Average and Adaptive likelihood price policy tend to lower the price immediately once the product is not in great demand. 
These policies often drop prices around week 6 to week 8 and significantly increase sales afterward. 
Yet, with discounted prices, the average revenue does not outperform others. 
Figure 6 demonstrates the weekly sales figures for each model and validates this observation. 
For instance, the average long-term policy drops the price around 8 weeks for an immediate sales increase, but quickly panics and keeps lowering the price until the 40\% discount is reached. 
The models with a slower price markdown strategy perform best in total revenue generation.
